---
title: "Final RMarkdown"
author: "Sophia Wheelton"
date: "2025-??-??"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## General Information
Question: How much does gene expression of CDKN2A differ between human breast cancer tissue and healthy human breat tissue?

Hypothesis: We predict that the DNA from the tissue samples will differ significantly.

Possible visualizations and test statistic(s): We can use a bar plot to show how many of individuals with the gene have cancer and how many individuals with cancer do not have the gene. The test statistic will probably be a t-test because there are only two datasets. 
```{r cars}
summary(cars)
```

## Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r eval=FALSE}
# Load ggplot2
library(ggplot2)

# Create data
#I need to go through and count the information myself because I cannot figure out how to upload the data set. 
data <- data.frame(
  name=c("Gene 1","Gene 2","Gene 3","Gene 4") ,  
  value=c(3,12,5,18) #I need to update these numbers and titles
  )

# Barplot
ggplot(data, aes(x=name, y=value)) + 
  geom_bar(stat = "identity")

#The data set also had R code available to make some plots, including a bar and whisker plot, but I have not figured out how to read in the data yet for the code to be helpful. This accompanying code chunk calculates a mean variance trend and determines a log2 relationship. 
```

